The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-21 formalwriteup.tex
notation fixes

Throughout this paper, we work over an algebraically closed field $k$ of characteristic $p > 0$ and fix $n$ so that $p \mid n$.  Let $S_n$ denote the symmetric group on $n$ elements, $V = k^n$ its permutation representation, and $s_{ij} \in S_n$ the transposition permuting $i$ and $j$.  Fix a basis $y_0,\ldots,y_{n-1}$ for $V$ and a dual basis $x_0, \ldots, x_{n-1}$ for $V^*$.  Let $\h$ and $\h^*$ be the dual $(n - 1)$-dimensional $S_n$-representations which are subrepresentation and quotient of $V$ and $V^*$, respectively given by
\[
\h = \sspan\{y_i - y_j \mid i \neq j\} \text{ and } \h^* = V^*/(x_0 + \cdots + x_{n - 1}).
\]
The action of $S_n$ on $\h$ and $\h^*$ is given explicitly by natural permutation of basis vectors.

Fix constants $\hbar$ and $c$ in $k$.  Denoting the tensor algebra of $\h \oplus \h^*$ by $T(\h \oplus \h^*)$, the \textit{type $A_{n - 1}$ rational Cherednik algebra} $\HH_{\hbar, c}(\h)$ is the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
\begin{align*}
[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{k=0}^{n-1}\sum_{l=0}^{n-1} c\langle y_i,x_k-x_l \rangle\langle y_k-y_l,x_j\rangle s_{kl}
\end{align*}
for all $0 \le i,j \le n-1$.  There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.  In addition, $\HH_{\hbar, c}(\h)$ admits a PBW decomposition 
\[
\HH_{\hbar,c}(\h) = \Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*).
\]
For any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)$ and $\HH_{\alpha\hbar,\alpha c}(\h)$ are isomorphic as algebras, so only the cases $\hbar = 0$ or $\hbar = 1$ need be considered.  In this paper, we restrict our attention to $\hbar = 1$.

@@

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.  The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
\end{align*}
where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
\[
D_{y_i - y_j} = \hbar \frac{\partial}{\partial (y_i-y_j)}-c\left(\sum_{k \ne i} \frac{1-s_{ki}}{x_i-x_k}\right)-c\left(\sum_{k \ne j} \frac{1-s_{ki}}{x_j-x_k}\right)
\]

where $\frac{\partial}{\partial (y_i-y_j)}$ is a differential operator we compute by letting $\frac{\partial x}{\partial (y_i-y_j)} = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$. 
\todo[inline]{Remove $D_i$ and replace the quantity above}

@@

For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.  For $i = 0, \ldots, n - 2$, define the formal power series
\[
F_i(z)=\frac{1}{1-x_iz} \left(\sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
\]
where $\binom{c}{k} = \frac{c (c - 1) \cdots (c - k + 1)}{k!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.

@@

In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG, CE}.  There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal ideal is known.
\begin{proposition}[{\cite[Proposition 3.1]{CE}}] \label{prop:ce}
If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal ideal $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
\[
\Res_\infty\left[\frac{dz}{z-x_j} \prod_{i=0}^{n-1} (z-x_i)^c\right] \text{ for $j=0,\dots,n-2$}.
\]
\end{proposition}
We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then taking $c = \frac{p}{n}$ should correspond to taking generic $c$.  While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.  By using a power series version of this construction of generators which  makes sense in characteristic $p$, we are able to mimic the arguments of \cite{BEG, CE} to show that they cut out a complete intersection and generate the entire ideal.  We believe that the philosophy of taking characteristic $p$ analogues of characteristic $0$ results for the rational Cherednik algebra should apply more generally and hope to explore this further in future work.

@@

Define the polynomials 
\[
g(z)=\prod_{j=0}^{n-1} (1-x_jz) \qquad \text{ and } \qquad F(z) = \sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k.
\]
In terms of $g(z)$ and $F(z)$, we have $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We will show that $f_i$ are singular vectors.

@@

\begin{lemma}\label{lem:z2g}
We have $[z^0]g(z)=1$ and $[z^1]g(z)=0$, meaning $z^2 \mid g(z)-1$.
\end{lemma}
\begin{proof}
Consider the expansion 
\[
g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+(-1)^nz^ne_n(x_0, \ldots, x_{n - 1})
\]
for the elementary symmetric polynomials $e_2, \ldots, e_n$.  Recalling that $\sum_i x_i=0$ by hypothesis, we see that $[z^1]g(z)=0$ and $[z^0]g(z)=1$, so $z^2 \mid g(z)-1$ as desired.
\end{proof}

\begin{lemma}\label{lem:dFdz}
We have
\[
F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z)
\]
such that $V(z)$ is a power series with $[z^l]V(z)=0$ for $l=0,\dots,p-1$. 
\end{lemma}

\begin{proof}
We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$. We compute
\begin{align*}
\frac{\partial F}{\partial z}
&=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
&=-\sum_j \frac{x_j}{1-x_jz}\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}(g-1+1)\\
&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1}.
\end{align*}
Defining the formal power series
\[
V(z)=\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1},
\]
we see that 
\[
F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z).
\]
It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.  By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$. Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
\end{proof}

\begin{lemma}\label{lem:dFdxi} We have
\[
\frac{\partial F}{\partial(y_1-y_0)} = G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
\]
such that $G(z)$ is a power series with $[z^l]G(z)=0$ for $l=0,\dots,p$. 
\end{lemma}

@@

We see that
\[
\frac{\partial g}{\partial(y_1-y_0)}=-\frac{zg}{1-x_1z}+\frac{zg}{1-x_0z}.
\]
Then we see that
\begin{align*}
\frac{\partial F}{\partial(y_1-y_0)}&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial (y_1-y_0)}\\
&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
\end{align*}
We define
\[
G(z)=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that
\[
\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
\]
It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$. By definition of $G(z)$, we see that $z(g-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$. Since $p \ge 2$, this implies $z^{p+1} \mid G(z)$, completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:ann} 
The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
\end{proposition}
\begin{proof}
We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.

We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$. It therefore suffices to consider the action of the Dunkl operators on $f_0$. We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.

By Lemma~\ref{lem:dFdxi} we recall that $\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.

We can now calculate $\frac{\partial F_0}{\partial (y_1-y_0)}$. We compute
\begin{align*}
\frac{\partial F_0}{\partial (y_1-y_0)}
&=-\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial (y_1-y_0)}\\
&=-\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(\frac{zc}{1-x_0z}-\frac{zc}{1-x_1z}\right)F(z)+\frac{G(z)}{1-x_0z}\\
&=\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)+\frac{G(z)}{1-x_0z}.
\end{align*}
We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).
\end{align*}
We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We see that 
\[
D_1-D_0=\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)
\]
since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute
\begin{align*}
(D_1-D_0)F_0&=\left(\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)\right)(F_0)\\
&=\frac{\partial F_0}{\partial (y_1-y_0)}-c\sum_{j > 1} \left(\frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{G(z)}{1-x_0z}+\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)-\sum_{j > 1} \frac{zc}{1-x_jz}F_0(z)\\
&=\frac{G}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
\end{align*}

In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.

@@

From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
&=\frac{G(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\&=\frac{G(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
\end{align*}

>>>>

Throughout this paper, we work over an algebraically closed field $k$ of characteristic $p > 0$ and fix $n$ so that $p \mid n$.  Let $S_n$ denote the symmetric group on $n$ elements, $V = k^n$ its permutation representation, and $s_{ij} \in S_n$ the transposition permuting $i$ and $j$.  Fix a basis $y_1,\ldots,y_{n}$ for $V$ and a dual basis $x_1, \ldots, x_{n}$ for $V^*$.  Let $\h$ and $\h^*$ be the dual $(n - 1)$-dimensional $S_n$-representations which are subrepresentation and quotient of $V$ and $V^*$, respectively given by
\[
\h = \sspan\{y_i - y_j \mid i \neq j\} \text{ and } \h^* = V^*/(x_1 + \cdots + x_{n}).
\]
The action of $S_n$ on $\h$ and $\h^*$ is given explicitly by natural permutation of basis vectors.

Fix constants $\hbar$ and $c$ in $k$.  Denoting the tensor algebra of $\h \oplus \h^*$ by $T(\h \oplus \h^*)$, the \textit{type $A_{n - 1}$ rational Cherednik algebra} $\HH_{\hbar, c}(\h)$ is the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
\begin{align*}
[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{m=1}^{n}\sum_{l=1}^{n} c\langle y_i,x_m-x_l \rangle\langle y_m-y_l,x_j\rangle s_{ml}
\end{align*}
for all $1 \le i,j \le n$.  There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.  In addition, $\HH_{\hbar, c}(\h)$ admits a PBW decomposition 
\[
\HH_{\hbar,c}(\h) = \Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*).
\]
For any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)$ and $\HH_{\alpha\hbar,\alpha c}(\h)$ are isomorphic as algebras, so only the cases $\hbar = 0$ or $\hbar = 1$ need be considered.  In this paper, we restrict our attention to $\hbar = 1$.

@@

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.  The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{(1-s_{ml}) f}{x_m - x_l},
\end{align*}
where we note that $\frac{(1-s_{ml}) f}{x_m - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
\[
D_{y_i - y_j} = \hbar \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mi}}{x_j-x_m}
\]

where $\partial_{y_i-y_j}$ is a differential operator we compute by letting $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$.

We note that we can extend the Dunkl operators $D_y$ to formal power series in $z$ with coefficients from $A$ by letting the Dunkl operators act on each coefficient of the power series.

@@

For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$. We present some power series as rational functions which we expand near $z=0$. For $i = 1, \ldots, n - 1$, define the formal power series
\[
F_i(z)=\frac{1}{1-x_iz} \left(\sum_{m=0}^{p-1} \binom{c}{m}(-1+\prod_{j=1}^{n} (1-x_jz))^m\right),
\]
where $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.

@@

In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG, CE}.  There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal ideal is known.
\begin{proposition}[{\cite[Proposition 3.1]{CE}}] \label{prop:ce}
If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal ideal $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
\[
\Res_\infty\left[\frac{dz}{z-x_j} \prod_{i=1}^{n} (z-x_i)^c\right] \text{ for $j=1,\dots,n-1$}.
\]
\end{proposition}
We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then taking $c = \frac{p}{n}$ should correspond to taking generic $c$.  While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.  By using a power series version of this construction of generators which makes sense in characteristic $p$, we are able to mimic the arguments of \cite{BEG, CE} to show that they cut out a complete intersection and generate the entire ideal.  We believe that the philosophy of taking characteristic $p$ analogues of characteristic $0$ results for the rational Cherednik algebra should apply more generally and hope to explore this further in future work.

@@

Define the polynomials 
\[
g(z)=\prod_{j=1}^{n} (1-x_jz) \qquad \text{ and } \qquad F(z) = \sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m.
\]
In terms of $g(z)$ and $F(z)$, we have $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We will show that $f_i$ are singular vectors.

@@

\begin{lemma}\label{lem:z2g}
We have $[z^0]g(z)=1$ and $[z^1]g(z)=0$, meaning $z^2 \mid g(z)-1$.
\end{lemma}
\begin{proof}
Consider the expansion 
\[
g(z)=\prod_{j=1}^{n} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_1, \ldots, x_{n})+\dots+(-1)^nz^ne_n(x_1, \ldots, x_{n})
\]
for the elementary symmetric polynomials $e_2, \ldots, e_n$.  Recalling that $\sum_i x_i=0$ by hypothesis, we see that $[z^1]g(z)=0$ and $[z^0]g(z)=1$, so $z^2 \mid g(z)-1$ as desired.
\end{proof}

\begin{lemma}\label{lem:dFdz}
We have
\[
F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z)
\]
such that $V(z)$ is a power series with $[z^l]V(z)=0$ for $l=0,\dots,p-1$. 
\end{lemma}

\begin{proof}
We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$. We compute
\begin{align*}
\frac{\partial F}{\partial z}
&=\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\frac{\partial g}{\partial z}\\
&=-\sum_j \frac{x_j}{1-x_jz}\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}(g(z)-1+1)\\
&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=1}^{p-1}c\binom{c-1}{m-1}(g(z)-1)^{m}\right)\\
&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g(z)-1)^{p-1}+\sum_{m=0}^{p-1}c\binom{c}{m}(g(z)-1)^{m}\right)\\
&=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g(z)-1)^{p-1}.
\end{align*}
Defining the formal power series
\[
V(z)=\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g(z)-1)^{p-1},
\]
we see that 
\[
F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z).
\]
It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.  By definition of $V(z)$, we see that $(g(z)-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$. Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
\end{proof}

\begin{lemma}\label{lem:dFdxi} We have
\[
\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)
\]
such that $G(z)$ is a power series with $[z^l]G(z)=0$ for $l=0,\dots,p$. 
\end{lemma}

@@

We see that
\[
\partial_{y_2-y_1}(g(z))=g(z)\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right).
\]
Then we see that
\begin{align*}
\partial_{y_2-y_1}(F(z))&=\left(\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\right)\partial_{y_2-y_1}(g(z))\\
&=\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)\left(\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\right)g(z)\\
&=\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m+1}\right)\\
&=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}+F(z)\right).
\end{align*}
We define
\[
G(z)=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}\right).
\]
Then we see that
\[
\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)
\]
It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$. By definition of $G(z)$, we see that $z(g(z)-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$. Since $p \ge 2$, this implies $z^{p+1} \mid G(z)$, completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:ann} 
The elements $f_i$ for $i=1,\dots,n-1$ are singular vectors in $A$.
\end{proposition}
\begin{proof}
We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.

We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$. It therefore suffices to consider the action of the Dunkl operators on $f_1$. We note that the Dunkl operators $D_{y_i-y_j}$ for all $i \ne j$ are spanned by $D_{y_i-y_1}$ for $1<i \le n$; then because $f_1$ is symmetric in the $x_i$ with $i > 1$, we see that it suffices to consider the action of $D_{y_2-y_1}$ on $f_1$ to show that the $f_i$ are annihilated by $D_{y_i-y_j}$ for all $i \ne j$.

By Lemma~\ref{lem:dFdxi} we recall that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.

We can now calculate $\partial_{y_2-y_1}(F_1(z))$. We compute
\begin{align*}
\partial_{y_2-y_1}(F_1(z))
&=-\frac{z}{(1-x_1z)^2}F(z)+\frac{1}{1-x_1z}\partial_{y_2-y_1}(F(z))\\
&=-\frac{z}{1-x_1z}F_1(z)+\frac{1}{1-x_1z}\left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_2z}\right)F(z)+\frac{G(z)}{1-x_1z}\\
&=\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{G(z)}{1-x_1z}.
\end{align*}
We note that $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{1i}$ for $1 < i \le n$. We see that 
\begin{align*}
\frac{1-s_{1i}}{x_1-x_i}(F_1(z))
&=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)\\
&=\frac{z}{(1-x_iz)(1-x_1z)}F(z)\\
&=\frac{z}{1-x_iz}F_1(z).
\end{align*}
We recall that we need only consider the action of $D_{y_2-y_1}$ on $F_1(z)$. We see that 
\[
D_{y_2-y_1}=\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}
\]
since $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. We now compute
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)(F_1(z))\\
&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}(F_1(z))+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}(F_1(z))\\
&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z).
\end{align*}

In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_1}{\partial z}$.

@@

From this it follows that
\begin{align*}
\frac{\partial F_1}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right)\\
&=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z}+\frac{1}{1-x_1z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
\end{align*}
We now again consider $D_{y_2-y_1}(F_1(z))$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_1(z)$ since that is $0$ in characteristic $p$. 
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z)+\left(\sum_{j} -zcF_1(z)+\frac{zc}{1-x_jz}F_1(z)\right)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)+\frac{-x_1z^2}{1-x_1z}F_1(z)+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\right)\\&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}.
\end{align*}
